---
title: "Session 2 Warm-Up"
output: 
  html_notebook:
    toc: yes
    toc_float: yes
---

## Introduction

In this Notebook you'll practice importing some data into R and making a map.

TIP: Use the workshop materials we saw last time, including slides, notebooks, and datasets description.

\

## 1) List the Layers in a File Geodatabase

There's a file geodatabase in the 'data' folder called `yose_communications.gdb`.

Write an expression that returns the layers in this geodatabase. [Hint](https://bit.ly/3N5IExu). [Answer](https://bit.ly/3FG495z)

```{r chunk01}
## Your answer here

```

\

## 2) Import the Cell Towers

Import the `Cell_Towers` layer, which is a point layer. [Answer](https://bit.ly/3L4FOrb)

```{r chunk02}
## Your answer here

```

\

How many cell towers are in the layer? [Hint](https://bit.ly/3LbHb7s). [Answer](https://bit.ly/3LnHpJ7)

```{r chunk03}
## Your answer here

```

\

What projection is it in? [Hint](https://bit.ly/3LezT2W). [Answer](https://bit.ly/3FJ3WOZ)

```{r chunk04}
## Your answer here

```

\

## 3) Make a plot of the cell towers:

[Solution](https://bit.ly/38l9kvM)

```{r chunk05}
## Your answer here

```


