---
title: "Find Suitable Locations for a New Campsite in Yosemite"
output: 
  html_notebook:
    toc: yes
    toc_float: yes
---

In this Notebook we'll compute some zonal stats, computing the average slope and elevation of each watershed in YNP.

## Setup

Load the packages we'll need and set tmap mode to 'plot':

```{r chunk01}
library(sf)
library(raster)
library(dplyr)
library(tmap)
tmap_mode("plot")

## Load the conflicted package
library(conflicted)
conflict_prefer("filter", "dplyr", quiet = TRUE)
conflict_prefer("count", "dplyr", quiet = TRUE)
conflict_prefer("select", "dplyr", quiet = TRUE)
conflict_prefer("arrange", "dplyr", quiet = TRUE)

```

\

## Import Layers for Yosemite National Park

For this analysis we'll need the park boundary, the watersheds, and a DEM (elevation) of the park. At the same time, we'll project everything to UTM.

Begin by importing the layers (see also the notebook  :

```{r chunk02}
epsg_utm11n_wgs84 <- 32611
epsg_geo_wgs84 <- 4326

## Import the park boundary
bnd_fn <- "./data/yose_boundary.shp"
file.exists(bnd_fn)
yose_bnd_utm <- st_read(bnd_fn) %>% 
  st_transform(epsg_utm11n_wgs84)

yose_wtrshds_utm <- st_read("./data/yose_watersheds.gpkg", layer="calw221") %>% 
  st_transform(epsg_utm11n_wgs84)

```

Plot to verify:

```{r chunk03}
tm_shape(yose_wtrshds_utm) +
  tm_borders(col = "gray", lwd = 1) +
tm_shape(yose_bnd_utm) +
  tm_borders(col = "red", lwd = 2) +
tm_grid(lines = FALSE) +
tm_layout(legend.outside = TRUE,
          asp = 1.2)
```

## Import the DEM

We have elevation data in the form of a tile of SRTM data.

```{r chunk04}
srtm1305_fn <- "./data/srtm_13_05.tif"
file.exists(srtm1305_fn)

srtm1305_rst <- raster(srtm1305_fn)
srtm1305_rst
```
## Crop the DEM to the Park Boundary

We can crop the large DEM to the park boundary using `raster::crop()`. Remember that the raster and the layer for the crop area need to be in the same CRS, so we transform the park boundary to geographic coordinates.

```{r chunk05}
yose_bnd_ll <- yose_bnd_utm %>% st_transform(epsg_geo_wgs84)

yose_dem_rst_ll <- raster::crop(srtm1305_rst, yose_bnd_ll)

yose_dem_rst_ll
```

Plot to verify:

```{r chunk06}
tm_shape(yose_dem_rst_ll) +
  tm_raster(title = "Elevation (m)", style = "cont", n = 15, palette = terrain.colors(256)) +
tm_shape(yose_bnd_ll) +
  tm_borders(col = "red", lwd = 2) +
tm_legend(outside = TRUE)
```

## Reproject the Clipped Raster

Lastly, we need to project the park DEM into UTM using `projectRaster()` with the following arguments:

- `from`: the raster we want to project 
- `to`: omitted in this case (because we're supplying `crs` and `res`)  
- `crs`: pass a proj4 string  
- `res`: resolution in map units (which in the case of UTM is meters)  
- `method`: choose 'blinear' but the cell values (elevation MSL) are continuous, and we want the interpolated values to also be continuous  

```{r chunk07}
## Define the proj4 string for UTM 11N
utm11n_wgs84_proj4 <- "+init=epsg:32611"

yose_dem_rst_utm <- projectRaster(from = yose_dem_rst_ll, 
                              crs = CRS(utm11n_wgs84_proj4), 
                              res = 90, 
                              method = "bilinear")
yose_dem_rst_utm
```

Plot to make sure it worked:

```{r chunk08}
tm_shape(yose_dem_rst_utm) +
  tm_raster(title = "Elevation (m)", style = "cont", n = 15, palette = terrain.colors(256)) +
tm_shape(yose_bnd_utm) +
  tm_borders(col = "red", lwd = 2) +
tm_grid(lines = FALSE) +
tm_layout(legend.outside = TRUE,
          asp = 1.2)
```

CHALLENGE: Compute average elevation per watershed.

```{r chunk09}
## Your answer here
```

\

## Compute Slope

Slope is one of the criteria for our campsite. We can compute the slope from the DEM using the `raster::terrain()`:

```{r chunk10}
yose_slope_rst <- raster::terrain(yose_dem_rst_utm, opt="slope")
yose_slope_rst
```

Plot to make sure it worked. Note that slope is measured in [radians](https://en.wikipedia.org/wiki/Radian).

```{r chunk11}
tm_shape(yose_slope_rst) +
  tm_raster(title = "Slope (radians)", style = "cont", n = 15, palette = gray.colors(256)) +
tm_shape(yose_bnd_utm) +
  tm_borders(col = "red", lwd = 2) +
tm_grid(lines = FALSE) +
tm_layout(legend.outside = TRUE,
          asp = 1.2)
```
\

Compute average slope per watershed.

```{r chunk12}

```


## CHALLENGE: Add one more criteria

Add one more criteria - exclude areas within 100m of an existing campsite. Hint: campsites are included in the `yose_poi.shp` layer. [Answer](https://bit.ly/2OnnFxA)

```{r chunk13}

```

## End

Congratulations, you completed another R Notebook. 

Save your Notebook to generate a HTML preview of the code you ran.
